The SMT Competition 2015--2018

### 2018-10-19 2018/report/SMT-COMP.tex
Benchmark numbers

The original goals of the competition were to spur adoption of the
common, community-designed SMT-LIB format (see
Section~\ref{sec:smtlib}), and to spark further advances in SMT,
especially for verification~\cite{BdMS05}.  These, together with
providing a useful yardstick of performance for users and developers
of SMT solvers, are still its main goals to date.  The competition has
been successful in establishing SMT-LIB as the de~facto standard
language for SMT solvers.  In recent years, the focus in this regard
has shifted towards promoting some of the newer extensions of the
SMT-LIB language, such as its floating-point theory or algebraic
datatypes~\cite{BarFT-RR-17}.

The competition is organized under the direction of the SMT Steering
Committee, which appoints the competition chair.  (This appointment
should happen ``within 30 days from the end of the current edition of
the SMT workshop''~\cite{smt-bylaws} but in practice has often
happened later.)  The competition chair then assembles a team of
organizers, and distributes the work for the next edition of the
competition.
%
The SMT Workshop includes a block of time to present the competitors
and results of the competition.  The workshop is affiliated with a
different conference each year: with CAV in 2015, with IJCAR in 2016,
again with CAV in 2017, and with FLoC in~2018.  Consequently, its date
varies by several weeks.  Competition results were presented on
July~19 in 2015, on July~2 in 2016, on July~23 in 2017, and on July~13
in~2018.

@@

The competition rules are revised each year, and a (near final) draft
version of the rules is made public on the competition web site around
mid-April.  The competition chair has ultimate responsibility for the
rules, but changes are often preceded by discussions among the
organizers or within the SMT community.  Such discussions are
initiated by a Call for Comments that is sent out to the SMT-COMP
mailing list~\cite{smtcomp-mailinglist} typically in February or early
March.  Publicly, this call is the first harbinger of a new edition of
the SMT Competition.

@@

All problems used in the SMT Competition come from the SMT Library
(SMT-LIB).  This is a large collection of benchmark problems from
various sources.  The SMT Library is available from a public
repository~\cite{smtlib-repository}, and each new release is mirrored
on StarExec (see Section~\ref{sec:starexec}), the cluster on which the
competition runs.  Users of SMT solvers are encouraged to submit new
and interesting benchmarks to the library, which has grown from 1,352
benchmarks in 2005~\cite{BdMS05} to 347,011 benchmarks in 2018.

Benchmarks in the SMT Library are written in the SMT-LIB
language~\cite{BarFT-RR-17}, a text-based format that defines the
syntax and semantics of solver input and output.  This includes a
language for terms and formulas, and a command language for
interacting with SMT solvers.  For instance,
Figure~\ref{fig:smtlib-example} shows the example formula from
Section~\ref{sec:introduction} as a benchmark in SMT-LIB syntax.
In~2016, benchmarks were updated from version~2.0 to version~2.5 of
the SMT-LIB language, and since~2017, benchmarks are written in
version~2.6.  Fortunately, versions~2.5 and~2.6 are largely
backwards-compatible to 2.0, so that older solvers are still able to
compete with at most minor modifications.

@@

Additionally, the SMT Library distinguishes between \emph{incremental}
and \emph{non-incremental} benchmarks.  Non-incremental benchmarks
contain a single {\tt check-sat} command, which instructs the SMT
solver to determine the satisfiability of the benchmark.  (Valid
solver responses are {\tt sat}, {\tt unsat}, and {\tt unknown}.)
Incremental benchmarks exercise additional solver features, such as
the ability to retract assertions, and typically contain multiple {\tt
  check-sat} commands.  These benchmarks originate from applications
such as bounded model checking~\cite{TODO}, where SMT solvers interact
with other tools in a feedback loop.  The 2018 release of the SMT
Library contained 336,844 non-incremental benchmarks in 51 logics, as
well as~10,167 incremental benchmarks (with a total of nearly 32
million {\tt check-sat} commands) in 26 logics.
Table~\ref{table:smtlib} presents further data on the size of the SMT
Library since~2015.  While the library usually grows from one year to
the next due to the inclusion of new benchmarks and logics, continuous
curation efforts may also cause benchmarks to be removed or
reclassified on occasion, thereby causing individual logics or even
the entire library to shrink.

\begin{table}
  \caption{Number of benchmarks and logics in the SMT Library}
  \label{table:smtlib}
  \centering
  \begin{tabular}{|r@{\ \ }l|r|r|r|r|}
    \hline
                               & & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    \multirow{2}{*}{Non-incremental $\{$} & benchmarks & 196,375 & 196,114 & 258,079 & 336,844 \\
                                          & logics     &      40 &      40 &      49 &      51 \\
    \multirow{2}{*}{Incremental $\{$}     & benchmarks &  10,019 &  10,024 &   6,262 &  10,167 \\
                                          & logics     &      15 &      15 &      22 &      26 \\
    \hline
  \end{tabular}  
\end{table}

@@

The SMT Competition consists of several tracks.  The \emph{main
  track}, which has been a staple of the competition since its
inception in 2005, features non-incremental benchmarks.  The
\emph{application track}, which has been part of the competition since
2011~\cite{TODO}, features incremental benchmarks.  These benchmarks
are passed to each solver one command at a time by a trace executor,
which waits for the solver's response before passing the next
benchmark command (to prevent look-ahead behavior).  The
\emph{unsat-core track} uses main-track benchmarks that are known to
be unsatisfiable, and solvers are evaluated on their ability to find
small unsatisfiable cores (i.e., a small but unsatisfiable subset of
the benchmark's assertions).  The unsat-core track had first been part
of the competition in 2012~\cite{TODO}, but was then discontinued
partly because of the competition's move to StarExec (see Section~5)
and lacking tool support.  It was re-introduced as an experimental
track in 2016, and has been a regular competition track since~2017.

Each track is further split into (logic) \emph{divisions}, where each
division corresponds to a logic from the SMT Library.  Participants
can choose which tracks and divisions they want to enter, and
competition results are reported separately for each track and
division.  Thus, competing solvers need not support all logics, and
may or may not support features such as incrementality or unsat-core
generation.

SMT Competitions until~2014 used a pseudo-random selection process to
cull the number of benchmarks used in the competition.  However, a
2013 evaluation found that this ``significantly lessens the ability of
a competition to determine `best'
solvers.''~\cite{DBLP:journals/jar/CokSW15} Together with the
increased computational resources available for the competition since
its move to StarExec, this prompted a paradigm shift.  Since 2015, the
competition is evaluating all solvers on all eligible benchmarks.
Some benchmarks from the SMT Library typically have to be excluded for
syntactic reasons: in 2015 and 2016, 11,966 benchmarks were excluded
because they contained partial or underspecified operations (e.g.,
bit-vector division) whose precise semantics were being debated at the
time.  Additionally in 2016, one benchmark was excluded because it
contained incorrect status information.  In 2017, 1,104 benchmarks
were excluded because their logic had been incorrectly classified, and
8 benchmarks were excluded because of incorrect or missing status
information.  In 2018, 3,603 benchmarks were excluded because they
contained named terms (a feature of the SMT-LIB language that is not
permitted in competition benchmarks), and 5 benchmarks were excluded
because of missing status information.

\begin{tjark}
  WIP: benchmark selection, tables with numbers, excluded benchmarks,
  unknown benchmarks
\end{tjark}

@@

% Local Variables:
% ispell-local-dictionary: "american"
% mode: LaTeX
% mode: flyspell
% LocalWords: concours hors satisfiability SMT Tjark
% End:

>>>>

The original goals of the SMT Competition were to spur adoption of the
community-designed SMT-LIB format (see Section~\ref{sec:smtlib}), and
to spark further advances in SMT, especially for
verification~\cite{BdMS05}.  These, together with providing a useful
yardstick of performance for users and developers of SMT solvers, are
still its main goals to date.  The competition has been successful in
establishing SMT-LIB as the de~facto standard language for SMT
solvers.  In recent years, the focus in this regard has shifted
towards promoting some of the newer extensions of the SMT-LIB
language~\cite{BarFT-RR-17}, such as floating-point numbers and
algebraic datatypes.

The competition is organized under the direction of the SMT Steering
Committee, which appoints the competition chair.  (This appointment
should happen ``within 30 days from the end of the current edition of
the SMT workshop''~\cite{smt-bylaws} but in practice has often
happened later.)  The competition chair then assembles a team of
organizers, and distributes the work for the next edition of the
competition.
%
The SMT Workshop includes a block of time to present the competitors
and results of the competition.  The workshop is affiliated with a
major conference in the field of automated reasoning each year: with
CAV in 2015, with IJCAR in 2016, again with CAV in 2017, and with FLoC
in~2018.  Consequently, its date varies.  Competition results were
presented on July~19 in 2015, on July~2 in 2016, on July~23 in 2017,
and on July~13 in~2018.

@@

The competition rules are revised each year, and a (near final) draft
version of the rules is made public on the competition web site around
mid-April.  The competition chair has ultimate responsibility for the
rules, but changes are often preceded by discussions among the
organizers or within the SMT community.  Such discussions are
initiated by a Call for Comments that is sent out to the SMT-COMP
mailing list~\cite{smtcomp-mailinglist} in February or early March.
Publicly, this call is the first harbinger of a new edition of the SMT
Competition.

@@

All problems used in the SMT Competition come from the SMT Library
(SMT-LIB).  This is a large collection of benchmark problems from
various sources.  The SMT Library is available from a public
repository~\cite{smtlib-repository}, and each new release is mirrored
on StarExec, the cluster on which the competition runs.  Users of SMT
solvers are encouraged to submit new and interesting benchmarks to the
library, which has grown from 1,352 benchmarks in 2005~\cite{BdMS05}
to 347,011 benchmarks in 2018.

Benchmarks in the SMT Library are written in the SMT-LIB
language~\cite{BarFT-RR-17}, a text-based format that defines the
syntax and semantics of solver input and output.  This includes a
language for terms and formulas, and a command language for
interacting with SMT solvers.  For instance,
Figure~\ref{fig:smtlib-example} shows the example formula from
Section~\ref{sec:introduction} as a benchmark in SMT-LIB syntax.
In~2016, benchmarks were updated from version~2.0 to version~2.5 of
the SMT-LIB language.  Since~2017, benchmarks are written in
version~2.6.  Fortunately, versions~2.5 and~2.6 are largely
backwards-compatible to 2.0, so that older solvers are still able to
compete with at most minor modifications.

@@

Additionally, the SMT Library distinguishes between \emph{incremental}
and \emph{non-incremental} benchmarks.  Non-incremental benchmarks
contain a single {\tt check-sat} command, which instructs the SMT
solver to determine the satisfiability of the benchmark.  (Valid
solver responses are {\tt sat}, {\tt unsat}, and {\tt unknown}.)
Incremental benchmarks exercise additional solver features, such as
the ability to retract assertions, and typically contain multiple {\tt
  check-sat} commands.  These benchmarks originate from applications
such as bounded model checking~\cite{TODO}, where SMT solvers interact
with other tools in a feedback loop.

The 2018 release of the SMT Library contained 336,844 non-incremental
benchmarks in 51 logics, as well as~10,167 incremental benchmarks
(with a total of nearly 32 million {\tt check-sat} commands) in 26
logics.  Table~\ref{table:smtlib} presents further data on the size of
the SMT Library since~2015.  While the library usually grows from one
year to the next because of the inclusion of new benchmarks and
logics, continuous curation efforts may also cause benchmarks to be
removed or reclassified on occasion, thereby causing individual logics
or even the entire library to shrink.  From 2015--2018, the total
number of benchmarks has increased by 68\,\%.
Figure~\ref{fig:benchmark-sizes} shows how the file size of individual
benchmarks is distributed.  The largest benchmark in the 2018 release
has a size of 993~MiB; the total size of the library is 85~GiB.

\begin{table}
  \caption{Number of benchmarks and logics in the SMT Library}
  \label{table:smtlib}
  \centering
  \begin{tabular}{|r@{\ \ }l|r|r|r|r|}
    \hline
                               & & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    \multirow{2}{*}{Non-incremental $\{$} & benchmarks & 196375 & 196114 & 258079 & 336844 \\
                                          & logics     &     40 &     40 &     49 &     51 \\
    \multirow{2}{*}{Incremental $\{$}     & benchmarks &  10019 &  10024 &   6262 &  10167 \\
                                          & logics     &     15 &     15 &     22 &     26 \\
    \hline
  \end{tabular}
\end{table}

\begin{figure}
  \TODO \\
  \TODO \\
  \TODO \\
  \TODO \\
  \TODO \\
  \TODO \\
  \TODO \\

  \caption{Distribution of benchmark sizes in the SMT Library (2018).}
  \label{fig:benchmark-sizes}
\end{figure}

@@

The SMT Competition consists of several tracks.  The \emph{main
  track}, which has been a staple of the competition since its
inception in 2005, features non-incremental benchmarks.  The
\emph{application track}, which has been part of the competition since
2011~\cite{TODO}, features incremental benchmarks.  These benchmarks
are passed to each solver one command at a time by a trace executor,
which waits for the solver's response before passing the next
benchmark command (to prevent look-ahead behavior).  The
\emph{unsat-core track} uses main-track benchmarks that are known to
be unsatisfiable, and solvers are evaluated on their ability to find
small unsatisfiable cores (i.e., a small but still unsatisfiable
subset of the benchmark's assertions).  The unsat-core track had first
been part of the competition in 2012~\cite{TODO}, but was then
discontinued partly because of the competition's move to StarExec and
lacking tool support.  It was re-introduced as an experimental track
in 2016, and has been a regular competition track again since~2017.

Each track is further split into (logic) \emph{divisions}, where each
division corresponds to a logic from the SMT Library.
Table~\ref{table:divisions} shows the number of divisions in each
track since~2015.  Participants can choose which tracks and divisions
they want to enter, and competition results are reported separately
for each track and division.  Thus, competing solvers need not support
all logics, and may or may not support features such as incrementality
or unsat-core generation.

There are slightly fewer divisions than logics in the SMT Library
(Table~\ref{table:smtlib}) because not every logic contains benchmarks
eligible for the competition.  Some benchmarks typically have to be
excluded for syntactic reasons: in 2015 and 2016, 11,966 benchmarks
were excluded because they contained partial or underspecified
operations (e.g., bit-vector division) whose precise semantics were
being debated at the time.  Additionally in 2016, one benchmark was
excluded because it contained incorrect status information.  In 2017,
1,104 benchmarks were excluded because their logic had been classified
incorrectly, and 8 benchmarks were excluded because of incorrect or
missing status information.  Moreover, divisions containing datatypes
({\tt DT})---which were new in~2017---were excluded from the
unsat-core track because of lacking tool support.  In 2018, 3,603
benchmarks were excluded because they contained named terms (a feature
of the SMT-LIB language that is not permitted in competition
benchmarks), and 5 benchmarks were excluded because of missing status
information.

\begin{table}
  \caption{Number of divisions in each competition track}
  \label{table:divisions}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
    & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    Main track        &  40 & 40 & 49 & 50 \\
    Application track &  14 & 14 & 16 & 21 \\
    Unsat-core track  &  -- & 40 & 41 & 44 \\
    \hline
  \end{tabular}
\end{table}

SMT Competitions until~2014 employed a pseudo-random selection process
to further cull the number of benchmarks used in the competition.
However, a 2013 evaluation found that this ``significantly lessens the
ability of a competition to determine `best'
solvers.''~\cite{DBLP:journals/jar/CokSW15} Together with the
increased computational resources available for the competition since
its move to StarExec, this prompted a paradigm shift.  Since 2015, the
competition is evaluating all solvers on all eligible
benchmarks. \TODO: benchmark weights

Another paradigm shift concerns the treatment of benchmarks with
unknown status.  Because of the difficulty to judge solver responses
for such benchmarks, SMT Competitions until 2015 only used benchmarks
whose status was known (i.e., that had been solved previously by
existing SMT solvers).  In 2015, 30,717 non-incremental benchmarks
from the SMT Library were not used for the competition because their
status was unknown.  However, this approach was criticized for
favoring imitation of existing solvers over true innovation.  In~2016,
the SMT Library contained 29,724 non-incremental benchmarks with
unknown status; solver performance on these was evaluated but reported
separately.  Since 2017, all non-incremental benchmarks are eligible
for the competition's main track regardless of status, and they
directly affect the competition results.  Solver responses for such
benchmarks are assumed to be correct, unless there is a disagreement
between two or more (otherwise sound) solvers.  Benchmarks with
disagreements are removed from the competition results (see
Section~\ref{sec:results-disagreements} for further discussion).

For incremental benchmarks, the situation is different: an incremental
benchmark is ineligible for the application track if its first {\tt
  check-sat} command has unknown status.  Otherwise, the prefix of the
benchmark that only contains {\tt check-sat} commands with known
status is eligible.  The main reason for this difference is that the
competition tools for the application track (in particular, the trace
executor) have not been adapted yet to support {\tt check-sat}
commands with unknown status.

Tables~\ref{table:benchmarks-main-track}--\ref{table:benchmarks-unsat-core-track}
show the number of benchmarks that were used in each competition track
and division since 2015.  A dash indicates that no eligible benchmarks
were available, and hence the corresponding SMT-LIB logic was not
actually a competition division in that track and year.

\begin{table}
  \caption{Number of benchmarks used in the main track (by division)}
  \label{table:benchmarks-main-track}
  \centering
  \scalebox{.9}[.83]{\begin{tabular}{|l|r|r|r|r|}
    \hline
    Division & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    ABVFP      &     -- &     -- &      1 &     1 \\
    ALIA       &     42 &     42 &     42 &    42 \\
    AUFBVDTLIA &     -- &     -- &   1709 &  1709 \\
    AUFDTLIA   &     -- &     -- &    728 &   728 \\
    AUFLIA     &      4 &      4 &      4 &     4 \\
    AUFLIRA    &  19849 &  19849 &  20011 & 20011 \\
    AUFNIRA    &   1050 &   1050 &   1480 &  1480 \\
    BV         &     85 &     85 &   5151 &  5751 \\
    BVFP       &     -- &     -- &     24 &    24 \\
    FP         &     -- &     -- &     61 &    61 \\
    LIA        &    201 &    201 &    388 &   388 \\
    LRA        &    339 &    339 &   2419 &  2419 \\
    NIA        &      9 &      9 &     14 &    14 \\
    NRA        &   3788 &   3788 &   3811 &  3813 \\
    QF\_ABV    &  14720 &  14720 &  15061 & 15066 \\
    QF\_ABVFP  &     -- &     -- &  18129 & 18129 \\
    QF\_ALIA   &    134 &    139 &    139 &   139 \\
    QF\_ANIA   &      6 &      8 &      8 &     8 \\
    QF\_AUFBV  &     37 &     37 &     31 &    31 \\
    QF\_AUFLIA &   1009 &   1009 &   1009 &  1009 \\
    QF\_AUFNIA &     21 &     21 &     17 &    17 \\
    QF\_AX     &    551 &    551 &    551 &   551 \\
    QF\_BV     &  26414 &  26414 &  40043 & 40102 \\
    QF\_BVFP   &      7 &      7 &  17215 & 17215 \\
    QF\_DT     &     -- &     -- &   8000 &  8000 \\
    QF\_FP     &  34413 &  34413 &  40302 & 40300 \\
    QF\_IDL    &   2094 &   2094 &   2193 &  2193 \\
    QF\_LIA    &   5839 &   5839 &   6141 &  6947 \\
    QF\_LIRA   &      6 &      6 &      7 &     7 \\
    QF\_LRA    &   1626 &   1626 &   1649 &  1649 \\
    QF\_NIA    &   8475 &   8593 &  23876 & 23876 \\
    QF\_NIRA   &      2 &      2 &      3 &     3 \\
    QF\_NRA    &  10184 &  10245 &  11354 & 11489 \\
    QF\_RDL    &    220 &    220 &    255 &   255 \\
    QF\_SLIA   &     -- &     -- &     -- & 72705 \\
    QF\_UF     &   6649 &   6649 &   6650 &  7423 \\
    QF\_UFBV   &     31 &     31 &     31 &  1224 \\
    QF\_UFIDL  &    441 &    441 &    428 &   428 \\
    QF\_UFLIA  &    598 &    598 &    583 &   583 \\
    QF\_UFLRA  &   1627 &   1627 &   1284 &  1284 \\
    QF\_UFNIA  &      7 &      7 &      7 &     7 \\
    QF\_UFNRA  &     34 &     34 &     36 &    36 \\
    UF         &   2839 &   2839 &   7562 &  7562 \\
    UFBV       &     71 &     71 &    200 &   200 \\
    UFDT       &     -- &     -- &   4535 &  4527 \\
    UFDTLIA    &     -- &     -- &    303 &   303 \\
    UFIDL      &     68 &     68 &     68 &    68 \\
    UFLIA      &   8404 &   8404 &  10137 & 10137 \\
    UFLRA      &     25 &     25 &     15 &    15 \\
    UFNIA      &   2319 &   2319 &   3308 &  3308 \\
    \hline
    Total      & 154238 & 154424 & 256973 & 333241 \\
    \hline
  \end{tabular}}
\end{table}

\begin{table}
  \caption{Number of benchmarks used in the application track (by
    division)}
  \label{table:benchmarks-application-track}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
    Division & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    ALIA       &   24 &   24 &   24 &   24 \\
    ANIA       &    3 &    3 &    3 &    3 \\
    AUFNIRA    &   -- &   -- &   -- &  117 \\
    BV         &   -- &   -- &   -- &   17 \\
    LIA        &    6 &    6 &    6 &    6 \\
    QF\_ABV    &   -- &   -- &   -- &   15 \\
    QF\_ALIA   &   44 &   44 &   44 &   44 \\
    QF\_ANIA   &    5 &    5 &    5 &    5 \\
    QF\_AUFBV  &   -- &   -- &   -- &   10 \\
    QF\_AUFLIA &   72 &   72 &   72 &   72 \\
    QF\_BV     &   18 &   18 &   18 &  815 \\
    QF\_BVFP   &   -- &   -- &    2 &    2 \\
    QF\_FP     &   -- &   -- &    2 &    2 \\
    QF\_LIA    &   65 &   69 &   68 &   69 \\
    QF\_LRA    &   10 &   10 &   10 &   10 \\
    QF\_NIA    &   10 &   10 &   10 &   10 \\
    QF\_UFBV   &   -- &   -- &   -- & 2327 \\
    QF\_UFLIA  &  905 &  905 &  780 &  780 \\
    QF\_UFLRA  & 3331 & 3331 & 3056 & 3058 \\
    QF\_UFNIA  &    1 &    1 &    1 &    1 \\
    UFLRA      & 5358 & 5358 & 1870 & 1870 \\
    \hline
    Total      & 9852 & 9856 & 5971 & 9257 \\
    \hline
  \end{tabular}
\end{table}

\begin{table}
  \caption{Number of benchmarks used in the unsat-core track (by
    division)}
  \label{table:benchmarks-unsat-core-track}
  \centering
  \scalebox{1}[.93]{\begin{tabular}{|l|r|r|r|}
    \hline
    Division & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    ALIA       &     41 &     41 &     41 \\
    AUFBVDTLIA &     -- &     -- &     25 \\
    AUFLIA     &      3 &      3 &      3 \\
    AUFLIRA    &  19749 &  19771 &  19771 \\
    AUFNIRA    &   1046 &   1050 &   1053 \\
    BV         &     56 &     94 &   4937 \\
    LIA        &    191 &    233 &    233 \\
    LRA        &    319 &   1106 &   1539 \\
    NIA        &      3 &      4 &      4 \\
    NRA        &   3788 &   3801 &   3801 \\
    QF\_ABV    &   4644 &   4673 &   4677 \\
    QF\_ABVFP  &     -- &   3934 &   3934 \\
    QF\_ALIA   &     80 &     80 &     80 \\
    QF\_ANIA   &      8 &      8 &      8 \\
    QF\_AUFBV  &     31 &     25 &     25 \\
    QF\_AUFLIA &    516 &    516 &    516 \\
    QF\_AUFNIA &     15 &     12 &     12 \\
    QF\_AX     &    279 &    279 &    279 \\
    QF\_BV     &  17172 &  23732 &  25700 \\
    QF\_BVFP   &      6 &   3174 &   3174 \\
    QF\_DT     &     -- &     -- &   4422 \\
    QF\_FP     &  17213 &  20028 &  20026 \\
    QF\_IDL    &    816 &    816 &    816 \\
    QF\_LIA    &   2840 &   2844 &   3019 \\
    QF\_LIRA   &      5 &      5 &      5 \\
    QF\_LRA    &    633 &    671 &    683 \\
    QF\_NIA    &    316 &   3130 &   4842 \\
    QF\_NIRA   &      2 &      2 &      2 \\
    QF\_NRA    &   4948 &   5296 &   5357 \\
    QF\_RDL    &    113 &    113 &    113 \\
    QF\_UF     &   4100 &   4101 &   4330 \\
    QF\_UFBV   &     31 &     31 &    575 \\
    QF\_UFIDL  &    335 &    322 &    322 \\
    QF\_UFLIA  &    195 &    183 &    183 \\
    QF\_UFLRA  &    853 &    511 &    511 \\
    QF\_UFNIA  &      7 &      7 &      7 \\
    QF\_UFNRA  &     18 &     11 &     11 \\
    UF         &   2039 &   3316 &   3442 \\
    UFBV       &     53 &     97 &     97 \\
    UFDT       &     -- &     -- &   1863 \\
    UFIDL      &     62 &     57 &     57 \\
    UFLIA      &   8377 &   7714 &   7743 \\
    UFLRA      &     20 &     10 &     10 \\
    UFNIA      &   2318 &   2432 &   2457 \\
    \hline
    Total      &  93241 & 114233 & 130705 \\
    \hline
  \end{tabular}}
\end{table}

@@

% Local Variables:
% ispell-local-dictionary: "american"
% mode: LaTeX
% mode: flyspell
% LocalWords: concours hors logics satisfiability SMT Tjark
% End:
